Modeling the Java Card API (or Interface?) in B

### 2012-03-16 papers/B2012-work/javacardAPIpaper.tex

\begin{document}
\begin{frontmatter}
  \title{Modeling the Java Card API (or Interface?) in B} \author{A. Martins Moreira\thanksref{ALL}\thanksref{anamaria}}
  \address{DIMAp-UFRN, Natal, RN, Brazil} \author{Simone - Bruno - David \thanksref{coemail}}
  \address{DIMAp-UFRN, Natal, RN, Brazil} \thanks[ALL]{INES-CAPES-projeto GD?... o que mais?} \thanks[anamaria]{Email:
    \href{mailto:anamaria@dimap.ufrn.br} {\texttt{\normalshape
        anamaria@dimap.ufrn.br}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}

@@

In the context of the BSmart project, we are interested in the use of
B to develop Java Card~\cite{chen:2000} applications.  Java Card is a
restricted and optimized version of Java which allows memory and
processor constrained devices, such as smart cards, to store and run
small applications.  Java Card applications have characteristics
(small size and need for security) which make then good candidates for
formal development with the B method. They also present some
regularity of structure that induced our group into the definition of
a method and a tool which specialize B for development of such
applications, providing greater support for the developer than pure B
tools \cite{atelierB, proB}. They are the BSmart method and tool
presented in \cite{mainpapers}.

Previous works have also dealt with B for Java Card, \cite{BOM,
  JBTools e cia}, but none has, at our knowledge, specified Java Card
in B so that the formal development includes Java Card aspects. In the
first versions of BSmart \cite{}, these aspects were included by the code
ganerator, and in JBTools \cite{}, the generated code needed to be edited by
the developer to include these aspects.

These works lacked then the ability to formally verify the Java Card
dependent aspects of the application. To be able to change this, a B
specification of these aspects is needed, and this contribution is
what we present in this paper: the B specification of the Java Card
API, with...  This specification can be used with the BSmart tool,
independently, in any B tool, or even as a complement to the official
Java Card documentation \cite{}.

>>>>

\begin{document}
\begin{frontmatter}
%  \title{Modeling the Java Card API (or Interface?) in B} \author{A. Martins Moreira\thanksref{ALL}\thanksref{anamaria}}
%  \address{DIMAp-UFRN, Natal, RN, Brazil} \author{S. de Oliveira Santos \thanksref{simone}}
%  \address{DIMAp-UFRN, Natal, RN, Brazil} \author{B. Emerson Gurgel Gomes \thanksref{bruno}}
%    \address{IFRN, Currais Novos, RN, Brazil} \author{D. Boris Paul D\'{e}harbe \thanksref{david}}
%      \address{DIMAp-UFRN, Natal, RN, Brazil} \thanks[ALL]{INES-CAPES-projeto GD?... o que mais?} \thanks[anamaria]{Email:
%    \href{mailto:anamaria@dimap.ufrn.br} {\texttt{\normalshape
%        anamaria@dimap.ufrn.br}}} 
%      \thanks[simone]{Email:
%    \href{mailto:simone82@ppgsc.ufrn.br} {\texttt{\normalshape
%        simone82@ppgsc.ufrn.br}}}
%      \thanks[bruno]{Email:
%    \href{mailto:bruno.gurgel@ifrn.edu.br} {\texttt{\normalshape
%        bruno.gurgel@ifrn.edu.br}}}
%       \thanks[david]{Email:
%    \href{mailto:david@dimap.ufrn.br} {\texttt{\normalshape
%        david@dimap.ufrn.br}}}

  \title{Modeling the Java Card API (or Interface?) in B} \author[ufrn]{A. Martins Moreira\thanksref{ALL}\thanksref{anamaria}}
  \author[ufrn]{S. de Oliveira Santos \thanksref{simone}}
  \author[ifrn]{B. Emerson Gurgel Gomes \thanksref{bruno}}
  \author[ufrn]{D. Boris Paul D\'{e}harbe \thanksref{david}}
  \address[ufrn]{DIMAp-UFRN, Natal, RN, Brazil} \thanks[ALL]{INES-CAPES-projeto GD?... o que mais? REUNI?}  \address[ifrn]{IFRN, Currais Novos, RN, Brazil} 
 \thanks[anamaria]{Email:
    \href{mailto:anamaria@dimap.ufrn.br} {\texttt{\normalshape
        anamaria@dimap.ufrn.br}}} 
      \thanks[simone]{Email:
    \href{mailto:simone82@ppgsc.ufrn.br} {\texttt{\normalshape
        simone82@ppgsc.ufrn.br}}}
      \thanks[bruno]{Email:
    \href{mailto:bruno.gurgel@ifrn.edu.br} {\texttt{\normalshape
        bruno.gurgel@ifrn.edu.br}}}
       \thanks[david]{Email:
    \href{mailto:david@dimap.ufrn.br} {\texttt{\normalshape
        david@dimap.ufrn.br}}}

@@

In the context of the BSmart project, we are interested in the use of
B to develop Java Card~\cite{chen:2000} applications.  Java Card is a
restricted and optimized version of Java which allows memory and
processor constrained devices, such as smart cards, to store and run
small applications.  Java Card applications have characteristics
(small size and need for security) which make then good candidates for
formal development with the B method. They also present some
regularity of structure that induced our group into the definition of
a method and a tool which specialize B for development of such
applications, providing greater support for the developer than pure B
tools \cite{atelierB,proB}. They are the BSmart method and tool
presented in \cite{Gomes10}.
%colocar o de 2008 também

Previous works have also dealt with B for Java Card, 
\cite{BOM,JBtools,e cia}, but none has, at our knowledge, specified Java Card
in B so that the formal development includes Java Card aspects. In the
first versions of BSmart \cite{Gomes10}, these aspects were included by the code
ganerator, and in JBTools \cite{JBtools}, the generated code needed to be edited by
the developer to include these aspects.

These works lacked then the ability to formally verify the Java Card
dependent aspects of the application. To be able to change this, a B
specification of these aspects is needed, and this contribution is
what we present in this paper: the B specification of the Java Card
API, with...  This specification can be used with the BSmart tool,
independently, in any B tool, or even as a complement to the official
Java Card documentation \cite{oracle}.
